\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Assignment 3 \hfill Spring 2019}}
\footline{Nathan Pickrell \hfill 31 January 2019 (Week 2 Lecture 2)\hfill 
Due: 5 February 2019 (Week 3 Lecture 1)}
% Lecture 3
\parindent 0pt

1.
Edit /etc/passwd entry

vim
bob:x:13101:1201:hw03:/home/bob:/bin/bash
sue:x:13102:1202:hw03:/home/sue:/bin/bash

2. 
Creat /etc/shadow password entry

bob:*:9797:0:::::
sue:*:9797:0:::::

3.
Set password

passwd bob
access31
passwd sue
access32

4.
Create home directory

mkdir ~bob
mkdir ~sue

5.
Copy .login and .bash_profile into the skeleton folder

cd ~djv
cp .login /etc/skel/
cp .bash_profile /etc/skel/

6.
Creat demo file

cd ~/etc/skel/
vim demo

"Hello there, welcome to CECS"

7.
Copy skeleton folder into bob and sue with reado only permission

cp -r /etc/skel/ ~bob
cp -r /etc/skel/ ~sue

8.
Set home directory permissions

chmod 755 ~bob
chmod 755 ~sue


check: 
pwd
ls -al

Purpose: This assignment is to familiarize you with setting up users and logins.

System Admin: When you submit assignment 2, you should ask for (and get)
a system administrator (root) account. If you didn't you will need to do so
when you start this assignment.

Submission: You will submit hw03.txt with ``\tilde grader/submit 03".
Put you name, account and machine on your document.
The document will contain the exact version of each command you did.
If you did an edit, tell me exactly what change you made to the file. 
You will leave the user login setup on your computer.

On the lab machine, you are assigned to administer set up the
following two accounts.
Do not use a script, do all the steps individually, by hand.

{\bf Account 1}:

Name {\ltt{}bob}
\break
Password: access31
\break
UID: {\ltt{}13101}
\break
Default group: {\ltt{}cecsu}
\break
Home directory: {\ltt{}/home/bob}

{\bf Account 2}:

Name {\ltt{}sue}
\break
Password: access32
\break
UID: {\ltt{}13102}
\break
Default group: {\ltt{}cecsg}
\break
Home directory: {\ltt{}/home/sue}

For {\it both} accounts:

Shell: {\ltt{}/bin/bash}
\break
Home directory contents, 3 files:
{\ltt{}.bash_profile}, {\ltt{}.login} and {\ltt{}demo}.
\break
The {\ltt{}.bash_profile} and {\ltt{}.login} files should be identical 
to those in the home directory of the {\ltt{}djv} account.
You should create the {\ltt{}demo} file using an editor
and it should contain one line of text saying,
``Hi there, welcome to CECS". 
(Note, this last file has no particular purpose other than
to make sure you know how to set up permissions and ownership correctly.)

The protection of the home directories should be 755.
The file ownership and group access of all files and directories
should be correctly set.
Because these groups come in over the network,
you will need to look at the {\ltt{}group} file on {\ltt{}cheetah}
for the group numbers.
Do not modify your local {\ltt{}group} file.

Note:
If you did not do so in Assignment 2,
you will need to look at the group file on cheetah to find out
the approriate group numbers for these accounts.

Testing:
\break
When the instructor grades your homework the following tests will be
performed on your assignment:
Login as your new user. Run {\ltt{}pwd} to make sure the home directory
is where it is supposed to be.
Run {\ltt{}ls -al} to make sure the files are there, that they have
the correct user and group and that your user doesn't own files
outside the user's home directory.
\bye
