\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Assignment 2 \hfill Spring 2019}}
\footline{Nathan Pickrell \hfill 29 January 2019 (Week 2 Lecture 1)\hfill 
Due: 31 January 2019 (Week 2 Lab 2)}
% due third session
\parindent 0pt

Purpose: This assignment is to familiarize you with users and logins.

Submission: You will submit hw02.txt with the ``\tilde grader/submit 02" 
command like in previous assigments.

Examine the password and group files on {\ltt{}cheetah}
and answer the following questions:

For the old instructor's account ({\ltt{}volper}) answer the following
questions:

1) What is the UID (user) number?

ssh cheetah
id -u volper

output:
100


2) What is the GID (group) number?

id -G volper

output:
300

3) What is the home directory?

echo ~volper

output:
/net/aardvark/u1/volper

4) What is the login shell?

echo $SHELL

output:
/bin/bash

5) What is the name of the base group the instructor belongs to?

id -Gn volper

output:
faculty

6) The user {\ltt{}djv} belongs to three additional groups,
what are the names of this group?

id -Gn djv

output:
faculty mail dialout users

7) What are the group numbers for the groups named {\ltt{}guest},
{\ltt{}cecsu} and {\ltt{}cecsg}?

cat /etc/group

output:
...
guest:x:60
cecsu:x:71
cecsg:x:72

Examine the shadow file on the {\ltt{}lab66} machine (Should be world
readable, if not, inform the instructor) and answer the following questions:

8) List the local accounts that have (encrypted) passwords.
Hint: there are a very small number of such accounts.

output:
root:$1$BB2sRjzi$Ik9DrblXMknCgOtwXKFBE/:16457:0:::::


9) When (approximately) was the password on the root account changed?
Give me a month and year. This will be approximate, that is, it
may be off by a couple days.

output:
January, 2015

Hint, use bc to help compute the year it was changed (assume
365.25 days per year), and roughly estimate the month 
(assume 30 days per month).

10) There is an alternate command available to show the password
age and expiry information on your machine (but not all Unix systems). 
Give this command.

chage -l root

11) Explain why marking the shadow file world readable is a poor decision.

The encryption strategy used to encrypt the password could be cracked in the future

Examine your {\ltt{}.bash_profile} and answer the following questions:

12) How many aliases are setup?

cat .bash_profile

output:
5
alias lf='ls -aCF'
alias l='ls -al'
alias ll='ls -al'
alias term='set noglob ; eval 'tset -rsQ \!*` ; set glob'
alias bye="logout"

13) How many directories in your path?

Modify your {\ltt{}.bash_profile}.
Remember, the {\ltt{}.bash_profile} file is only read when you login.
I recommend you modify in one window and use a second window
to login and test your changes (that way you won't lock yourself out).
Be sure to verify that your changes work.

echo $PATH

output:
/bin:/usr/bin:/bin:/usr/cecs/bin:/sbin:/usr/sbin:/usr/bin/X11:/usr/local/bin:.
9

14) Add an alias have {\ltt{}p} be a shorthand for {\ltt{}ps aux}. 
Give the command to do this.

vi .bash_profile
alias p='ps aux'



15) Add the directory {\ltt{}~djv} to the end of your path.
After you have done this, from your home directory, you should be
able to run the {\ltt{}hello} program (which prints {\ltt{}Hello}).
This program exists only in the {\ltt{}~djv} directory. 

vi .bash_profile
- added path to end
hello

\bye
