\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Assignment 9 \hfill Spring 2019}}
\footline{Nathan Pickrell \hfill 21 February 2019 (Week 5 Lecture 2)\hfill 
Due: 26 February 2019 (Week 6 Lab 1)}
\parindent 0pt

Purpose: This assignment covers backups and termcap.

{\bf Backups---}

{\bf tar:}
Make a tar back up of the home directory of your user (bob) to your 
removable device (floppy or flashdrive).
Confirm that the backup was made using the {\ltt{}t} option.

Note: This is a tar device not a tar file. It does not have a 
directory structure, so no mkfs should be done; 
all information on the device before
the tar will be destroyed. After you do the backup, your
device will look like a tape.

1) Submit: the sequence of commands from login up through the
tar command that lists the tar contents.

{\bf tar, extracting an archive:}
Login as root, this puts you in {\ltt{}/root}.
Extract the contents of the compressed tar file {\ltt{}~djv/giant.tgz},
preserving the permissions.
(Note, this should build a directory called {\ltt{}giant} inside {\ltt{}/root}.)

--plug in flash drive--

tar -cf /dev/sdc1 ~bob/

tar -tf /dev/sdc1

tar -xpf ~djv/giant.tgz

ls --to make sure giant is there

2) Submission: The exact command you used.
Inside {\ltt{}giant} there are three subdirectories, submit: the names of
these three directories. (This lets me know you unwound the archive.)
Pick any of these subdirectories, you will find a file inside it,
submit: the name of the file, who owns the file, what group the file
belongs to and the access rights (the {\ltt{}rwx} stuff) for the file.
(This lets me know you preserved permissions.)

As root,
extract the contents of the compressed tar file {\ltt{}~djv/house.txz},
preserving the permissions.
(Note, this should build a directory called {\ltt{}house} inside {\ltt{}/root}.)

cd giant
ls

fee	fie	foe

cd fee
ls -al

drwxr-xr-x 2 djv faculty 4096 Feb 23 1998 .
drwxr-xr-x 5 djv faculty 4096 Feb 23 1998 ..
-rw-r--r-- 1 djv faculty   10 Feb 23 1998 fum

Name: fum
Owner:djv
Group: faculty
Rights: -rw-r--r--


3) Submission: The exact command you used. The contents
of the file called {\ltt{}wolf}.

tar -xpf ~djv/house.txz

ls --to check if house is there

cd house
ls

bricks	sticks	straw

cd bricks
ls

wolf

cat wolf

Huff and puff


{\bf Encryption:}
The file is encrypted using gpg with the passphrase {\ltt{}troll}.
Decrypt the file {\ltt{}~djv/joe.cr}.

4) Submit: the contents of the file.

gpg -d ~djv/joe.cr

--type troll for passphrase--

Hi there joe


{\bf Terminals---}

5) Termcap.
On the linux console: what sequence is used to 
start underlining?
%clear from the current cursor position to the end of line

man termcap | grep under

us Start underlining

vim /etc/termcap

:us=\E[36m


6) stty.
On the linux console: what key is used to stop (pause) the output to the
screen?
What command would you give to define control-Y to be the key used
to stop the output?

stty --all

stop = ^S

stty stop ^Y --key used to stop the output--

\bye
